\vspace{3cm} \Huge{Optimizing SasView models} \\ \Large{Enhancing performance by rewriting kernels from OpenCL/OpenMP to Futhark}

### 2017-11-08 report/draft.tex
kk

However, when we work with the rewritten core shell parallelepiped, we see huge
speedups even at n=100. This 
FUTHARK-MAGI HOISTING OG TING PÅ MAPS

% show core_shell-whatever; and elaborate on loop flattening into maps
%%% MASSER AF REFERENCER TIL TROELS' PAPERS

\subsection{Correctness of Futhark results}

>>>>

However, when we work with the rewritten core shell parallelepiped, we see huge
speedups even at n=100. This speedup mainly comes from Futharks ## INDSÆT DET 
DER FEDE NOGET MED MAPS.
Looking at the definition of core_shell_parallelepiped_futhark, we see that 11
parameters are extracted from the local\_values array. We could fear that this
happens for every application of Iq, but the Futhark compiler actually performs
HOISTING, which is an optimization that rewrites the program internally, so that
these variable allocations are moved out of the Iq function, and are thus only
performed once, instead of n times.
# KIIIIIIIIIILDE

\subsection{Correctness of Futhark results}
There has been one small issue with the correctness of the Futhark models.
As the Futhark models are generic by design, and instantiated with the 
programmer's floating point type of choice, we can run the Futhark kernels
with any precision we want.

However, some of the original \sasmodels models have Iq functions that are 
hardcoded to use double precision floats in places, and even sometimes mixes
doubles and singles. 
As these models plays fast and loose with the precision type, the Futhark models
will inevitably end up showing some total difference between it's results and 
the results from the built in functions.

However, several \sasview users have assured me, that it is not really a 
problem. The worst examples of these differences has been accumulated errors of
between 10e-6 and 10e-7, which is well within the error range accepted by 
the \sasview users.
